---
title: "P8105 Homework 6"
author: "Pengyuan Su (ps3195)"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(purrr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(mgcv)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

**import and tidy**

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  mutate(
    across(
      c("frace", "mrace"),
      ~ case_when(
        .x == 1 ~ "White",
        .x == 2 ~ "Black",
        .x == 3 ~ "Asian",
        .x == 4 ~ "Puero Rican",
        .x == 8 ~ "Other",
        .x == 9 ~ "Unknown"
      )
    ),
    babysex = case_when(
      babysex == 1 ~ "White",
      babysex == 2 ~ "Black"
    ) %>% as.factor(),
    malfrom = case_when(
      malform == 0 ~ "absent",
      malform == 1 ~ "present"
    ) %>% as.factor(),
    across(where(is.character), as.factor)
  )
```

**fit a model**

I will use stepwise to choose a model, it is choosing a model by AIC in a stepwise algorithm.

```{r stepwise}
model1 = 
  lm(bwt ~ ., data = baby_df) %>% 
  step(trace = 0)

summary(model1)

```

And the results suggest that the pick by stepwise is:

bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken
    
```{r set model}
fit_model = 
   lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = baby_df)
```

```{r}
baby_df %>% 
  add_predictions(fit_model) %>% 
  add_residuals(fit_model) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm",) +
  labs(x = 'fitted values of birthweight', y = 'model residuals', title = 'Model residuals against fitted values')
```

The plot shows that there may be no linear relationship between fitted values and residuals of models since the lm-smooth line is extremely close to the x-axis. Also, center of model residuals' distribution is around 0.


**Other Model**

Model 1: bwt ~ blength + gaweeks

Model 2: bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex


**Cross validation:**

```{r}
set.seed(51)

cv = 
  modelr::crossv_mc(baby_df, 200, id = "id") %>% 
  mutate(
    model_main = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_1 =  map(.x = train,  ~ lm(bwt ~ blength + gaweeks, data = .x)),
    model_2 = map(.x = train,  ~ lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_main = map2_dbl(.x = model_main, .y = test, ~rmse(.x, .y)),
    rmse_1 = map2_dbl(.x = model_1, .y = test, ~rmse(.x, .y)),
    rmse_2 = map2_dbl(.x = model_2, .y = test, ~rmse(.x, .y))
  )

cv %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(
        title = "Cross Validation Comparisons",
        x = "Models",
        y = "RMSE")
```

It seems that my model has the lowest rmse among these three models, and the second model is better than the first model since it has lower rmse.


## Problem 3

**Read and tidy data**

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm")
```


